\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{booktabs}
\usepackage{hyperref}
\title{See Sight Tours Dashboard Report}
\author{Abdul Moiz Ghazanfar \& Munhib Baig}
\date{\today}

\begin{document}

\maketitle

\section*{1. Overview}
This report presents an analysis of the performance metrics for \textbf{See Sight Tours}, using insights extracted from a Power BI dashboard. The report covers tour popularity, revenue distribution, and regional performance across several cities in North America.

\section*{2. Top Performing Tours}
The dashboard highlights the most popular tours based on income or booking volume:
\begin{itemize}
    \item Best of Niagara Falls Tour – \textbf{1.09M}
    \item Ultimate Niagara Falls Tour – \textbf{0.38M}
    \item Best of Toronto Tour – \textbf{0.14M}
    \item Best of San Antonio Tour – \textbf{0.14M}
    \item Day and Night Combo Tour – \textbf{0.14M}
\end{itemize}

\section*{3. Regional Tour Popularity}
Tour demand is highest in the following regions:
\begin{itemize}
    \item Niagara Falls, Canada (head office)
    \item San Antonio
    \item Toronto
    \item Montreal
    \item Chicago, Boston, Vancouver, Miami, Ottawa
\end{itemize}
These regions show varying levels of engagement across the months of January to July 2023.

\section*{4. Revenue and Expense Breakdown}
\subsection*{Account Distribution}
\begin{itemize}
    \item Revenue: \textbf{52\%}
    \item Operating Expenses: \textbf{34\%}
    \item COGS (Cost of Goods Sold): \textbf{14\%}
\end{itemize}

\subsection*{Revenue Streams}
\begin{itemize}
    \item Tour Income: \textbf{99.13\%}
    \item Other Income: \textbf{0.87\%}
\end{itemize}

\section*{5. Financial Trends (Jan--Jun 2023)}
\begin{itemize}
    \item \textbf{Revenue:} Ranged from negative values to a peak of \textbf{1.5M} in March.
    \item \textbf{Operating Expenses and COGS:} Followed a fluctuating trend, notably spiking or dipping based on revenue performance.
\end{itemize}

\section*{6. City-Level Performance}
Monthly financial performance (Revenue, COGS, and Expenses) was recorded for the following cities:
\begin{multicols}{2}
\begin{itemize}
    \item Austin
    \item Boston
    \item Charlettown
    \item Chicago
    \item Fort Lauderdale
    \item Halifax
    \item Miami
    \item Montreal
    \item Niagara Falls (Canada \& USA)
    \item Ottawa
    \item Philadelphia
    \item Saint John
    \item San Antonio
    \item Savannah
    \item St. Louis
    \item Toronto
    \item Vancouver
\end{itemize}
\end{multicols}

\section*{7. Conclusion}
The dashboard provides a comprehensive look at See Sight Tours’ operations and finances. Niagara Falls, Canada, continues to dominate in popularity and revenue. While Tour Income remains the primary revenue source, continued monitoring of COGS and operating expenses will be essential to sustain growth.

\end{document}
